---
title: Statcan data with cansim
---

# StatsCan Data Access with R

Using the [cansim](https://mountainmath.github.io/cansim/index.html) package.


```{r}
install.packages("cansim")
```

```{r}
library("cansim")
```

> Product Identification number (PID) is a unique product identifier for all Statistics Canada products, including large multidimensional tables. The first two digits refer to a subject, the next two digits refer to product type, the last four digits refer to the product itself.


Specify the product ID (PID) to retrieve the table displayed at https://www150.statcan.gc.ca/t1/tbl1/en/tv.action?pid=2710002201

```{r}
table <- get_cansim("271-000-22")
```

```{r}
tail(table)
```

Exploring a time series as a specific `VECTOR` is referred to as information along the time axis.

```{r}
# 2013-01-01 is date from which on the data is provided
get_cansim_vector("v54329358","2013-01-01")
```

Getting the meta data of the vector.

```{r}
get_cansim_vector_info("v54329358")
```

Finally, let's get a list of tables:

```{r}
head(list_cansim_tables())
```


