---
title: "Shiny Dashboards from Github"
output: html_document
---

# Launch a Shiny application from Github!

This example downloads a dashboard to run from Github. All you need are the dashboard's dependencies install and the `shiny` package. **Note, once you run it, you may need to enable popups**


To see some examples of Shiny apps, you can go to [the R-Dashbaords repository](https://github.com/StatCan/R-dashboards)

**To use this example, click the little "Run Chunk" arrow beside each code block**


## A Simple Example

```{r, eval=FALSE}
shinystuff = c("shiny", "shinyboard")
for (package in shinystuff) {
  print(package)
  if (!require(package, character.only=TRUE))
    install.packages(package)
}

shiny::runGitHub("shiny-examples", "rstudio", subdir = "005-sliders")

```

# An example from our repository

This next example requires `gdal` which take a while to install. Bear with it!!!

## Install the dependencies (conda is recommended)

```{sh, engine.path = '/bin/bash', eval=FALSE}
conda install --yes --use-local gdal r-rgdal
echo Done
```

```{r, eval=FALSE}
dependencies = c(
    "shiny",
    "shinyboard",
    "plotly",
    "shinycssloaders",
    "shinyjs",
    "shinythemes",
    "leaflet",
    "formatR",
    "shiny.i18n",
    "shinyWidgets",
    "rgdal",
    "sqldf",
    "cansim",
    "janitor"
)

for (package in dependencies) {
  print(package)
  if (!require(package, character.only=TRUE))
    install.packages(package)
}
```

# Run a dashboard!!!

**NOTE: You will get a pop-up, which you will need to enable.**

```{r, eval=FALSE}
shiny::runGitHub("R-dashboards", "statcan", subdir = "ev-data-viz")
```
