---
title: "Interacting with Bucket Storage with R + mc"
date: "`r Sys.Date()`"
abstract: This example combines R with mc for the simplest possible storage workflow.
---

# Before you begin

Make sure that you enabled Minio credential injection when you created this server!
Otherwise, you will have a hard time connecting.

**In the following, you will need to replace the name `blair-drummond` with your name.**

# Get Connected

We will use `standard` storage for this example, but the following applies mutatis mutandis to `premium`.


```{sh, engine.path = '/bin/bash'}
source /vault/secrets/minio-standard-tenant-1
mc config host add minio-standard $MINIO_URL $MINIO_ACCESS_KEY $MINIO_SECRET_KEY

# source /vault/secrets/minio-premium-tenant-1
# mc config host add minio-premium $MINIO_URL $MINIO_ACCESS_KEY $MINIO_SECRET_KEY
```

This will configure the access for you.

Then you proceed as in the examples!

## Create your bucket

Replace with your name!

```{sh, engine.path = '/bin/bash'}
mc mb -p minio-standard/blair-drummond
```

## Upload a file

```{sh, engine.path = '/bin/bash'}
mc cp example.txt minio-standard/blair-drummond/happy-bird.txt

mc cp -r example-folder minio-standard/blair-drummond/example-folder
```



## List objects

```{sh, engine.path = '/bin/bash'}
echo private:
mc ls minio-standard/blair-drummond/

echo
echo shared:
mc ls minio-standard/shared/blair-drummond/ || true
```


## Download a file

```{sh, engine.path = '/bin/bash'}
mc cp minio-standard/blair-drummond/happy-bird.txt downloaded-example.txt
```

# Example with RData files

You've seen how to upload, list, and download files.

Using this, you can do cool things like save and upload .Rdata files. For example.


```{r, fig.show='hold', eval=TRUE, include = TRUE}
# Create your .rds file
data("mtcars")
saveRDS(mtcars, "mtcars.rds")
```

## Upload it

```{sh, engine.path = '/bin/bash'}
mc cp mtcars.rds minio-standard/blair-drummond/mtcars.rds
```

## Download it

```{sh, engine.path = '/bin/bash'}
mc cp minio-standard/blair-drummond/mtcars.rds mtcars-two.rds
```

## Load it into R

```{r, fig.show='hold', eval=TRUE, include = TRUE}
mtcars_two <- readRDS("mtcars-two.rds")

head(mtcars_two)
```

That's it!
