---
title: "Interacting with Bucket Storage"
date: "`r Sys.Date()`"
---

# Before you begin

If you copy-paste this script for your own use, make sure that you also bring along the helper script `daaas_storage.R`.

# Upload and download files from storage

Many of these examples are straight from the R `aws.s3` library.

The difference is that instead of creating your own S3 Client object, you can just run:

```{r, fig.show='hold', eval=TRUE, include = TRUE}
source("daaas_storage.R")
daaas_storage.standard()
# daaas_storage.premium()
```

This will configure the access for you.

Then you proceed as in the examples!

**NOTE: use_https=FALSE, region="" are required, unfortunately.**

## Get Connected


```{r, fig.show='hold', eval=TRUE, include = TRUE}
install.packages("aws.s3")
library("aws.s3")
library("RJSONIO")
source("daaas_storage.R")

# And create the client connection
daaas_storage.standard()
```


## Create your bucket


```{r, fig.show='hold', eval=TRUE, include = TRUE}
#If Bucket already exists throws Error in parse_aws_s3_response(r, Sig, verbose = verbose) : Conflict (HTTP 409) which is acceptable.
#Replace with your name!
BUCKET = 'blair-drummond'
SECURE <- as.logical(Sys.getenv("SECURE"))
b <- put_bucket(BUCKET, use_https=SECURE, region="")
```


## Upload a file

```{r, fig.show='hold', eval=TRUE, include = TRUE}
put_object(
    file="example.txt",
    object="happy-bird.txt",
    bucket=BUCKET,
    show_progress = TRUE,
    use_https=SECURE,
    region=""
)

put_folder(
    folder="example-folder",
    bucket=BUCKET,
    show_progress = TRUE,
    use_https=SECURE,
    region=""
)
```



## List objects

```{r, fig.show='hold', eval=TRUE, include = TRUE}
get_bucket(bucket = BUCKET, use_https=SECURE, region="")
```


## Download a file


```{r, fig.show='hold', eval=TRUE, include = TRUE}
save_object(
    "happy-bird.txt",
    bucket=BUCKET,
    file="downloaded-example.txt",
    use_https=SECURE,
    region=""
)
```


# That's it!

You've seen how to upload, list, and download files.
You can do more things! For more advanced usage, check out the

[`aws.s3` package overview](https://cran.r-project.org/package=aws.s3).

And don't forget that you can also do this all on the commandline with `mc`
